BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-18 Msc-Slides/main.tex
Small changes here and there

It is hard to distinguish the calls made directly by the sample from the ones made within libraries
\begin{itemize}
\item Resulting logs are large and full of irrelevant information
\end{itemize}

@@

     \begin{beamerboxesrounded}[shadow=true]{Evasive malware}
Malware that conceals its harmful behaviour when detecting a
hostile environment, such as a well-known sandbox
solution
    \end{beamerboxesrounded}
    \bigskip
    \bigskip
    \begin{figure}
    	\vspace{-0.8cm}
    	\hspace*{0.5cm}
        \includegraphics[width=10cm]{image/evasive.pdf}
    \end{figure}
\vspace{-0.3cm}
Current tracing techniques are \textbf{easily detectable} and are not coupled with mechanisms to hide their presence

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Validation (1) with Al-Khaser}
    \begin{beamerboxesrounded}[shadow=true]{}
	\textbf{Al-Khaser} is an open-source application which performs common checks employed by malware families to determine if they are being
executed in an analysis environment.
\end{beamerboxesrounded}
\medskip
Checks divided in categories:
\begin{itemize}
\item \textbf{Anti-Debugging}
\item \textbf{Timing-based}
\item \textbf{Human Interaction Detection}
\item \textbf{Anti-Virtualization}
\item \textbf{Detection of Analysis Tools}
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
BlueTracer: 
\begin{itemize}
\item remained undetected thanks to its integration with BluePill
\item managed to track all the checks
\end{itemize}
\end{beamerboxesrounded}

@@

    \begin{table}[h]
\vspace*{-0.1cm}
\begin{center}
\resizebox{9.2cm}{!}{
 \begin{tabular}{||c c c||}
 \hline
 \textbf{ID} & \textbf{MD5} & \textbf{Name} \\ 
 \hline\hline
 1 & 0af4ef5069f47a371a0caf22ae2006a6 & \textit{banker} \\ 
 \hline
 2 & 9437eabf2fe5d32101e3fbf9f6027880 & \textit{dropper} \\
 \hline
 3 & cbdda646a20d95f078393506ecdc0796 & \textit{trojan}\\
 \hline
 4 & cfdd16225e67471f5ef54cab9b3a5558 & Olympic\\
 \hline
 5 & ef694b89ad7addb9a16bb6f26f1efaf7 & CCleaner\\ 
 \hline
\end{tabular}
}
\end{center}
\end{table}
\vspace{-0.1cm}
Evaluation was done manually and is a time-consuming process:
\begin{itemize}
\item Check if logs are congruous with Joe Security reports
\item Process Monitor as ground truth for system activity
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
The
logs collected by BlueTracer reveal behaviors consistent with the analysis reports
authored by Joe Security
\end{beamerboxesrounded}

>>>>

It is hard to distinguish the calls made directly by the sample from the ones made within libraries
\begin{itemize}
\item Resulting logs are large and contain irrelevant information
\end{itemize}

@@

     \begin{beamerboxesrounded}[shadow=true]{Evasive malware}
Malware that conceals its harmful behaviour when detecting a
hostile environment, such as a well-known sandbox
solution
    \end{beamerboxesrounded}
    \bigskip
    \bigskip
    \begin{figure}
    	\vspace{-0.8cm}
    	\hspace*{0.5cm}
        \includegraphics[width=10cm]{image/evasive.pdf}
    \end{figure}
\vspace{-0.3cm}
Current tracing tools are \textbf{easily detectable} and are not coupled with mechanisms to hide their presence

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Validation (1) with Al-Khaser}
    \begin{beamerboxesrounded}[shadow=true]{}
	\textbf{Al-Khaser} is an open-source application which performs common checks employed by malware families to determine if they are being
executed in an analysis environment.
\end{beamerboxesrounded}
\medskip
Many implemented techniques:
\begin{itemize}
\item \textbf{Anti-Debugging}
\item \textbf{Timing-based}
\item \textbf{Human Interaction Detection}
\item \textbf{Anti-Virtualization}
\item \textbf{Detection of Analysis Tools}
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
BlueTracer: 
\begin{itemize}
\item remained undetected thanks to its integration with BluePill
\item managed to track all the checks
\end{itemize}
\end{beamerboxesrounded}

@@

    \begin{table}[h]
\vspace*{-0.1cm}
\begin{center}
\resizebox{9.2cm}{!}{
 \begin{tabular}{||c c c||}
 \hline
 \textbf{ID} & \textbf{MD5} & \textbf{Name} \\ 
 \hline\hline
 1 & 0af4ef5069f47a371a0caf22ae2006a6 & \textit{banker} \\ 
 \hline
 2 & 9437eabf2fe5d32101e3fbf9f6027880 & \textit{dropper} \\
 \hline
 3 & cbdda646a20d95f078393506ecdc0796 & \textit{trojan}\\
 \hline
 4 & cfdd16225e67471f5ef54cab9b3a5558 & Olympic\\
 \hline
 5 & ef694b89ad7addb9a16bb6f26f1efaf7 & Malicious CCleaner\\ 
 \hline
\end{tabular}
}
\end{center}
\end{table}
\vspace{-0.1cm}
Evaluation was done manually and is a time-consuming process:
\begin{itemize}
\item Check if logs are congruous with Joe Security reports
\item Process Monitor as ground truth for system activity
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
The
logs collected by BlueTracer reveal behaviors consistent with the analysis reports
authored by Joe Security
\end{beamerboxesrounded}
